---
title: "eBird diversity finder"
output: html_notebook
---

# Find species-rich eBird locations


```{r}
install.packages("devtools")
devtools::install_github("ropensci/rebird")
```


Get a list of all counties for a region: not implemented in `rebird` yet.


First, get the eBird API token, which I stored in my `.Renviron` file as `EBIRD_KEY`.
If you don't have an `.Renviron` file, you can make one in several locations, but I made mine in the location determined by running `Sys.getenv("HOME")`

```{r}
EBIRD_KEY <- Sys.getenv("EBIRD_KEY")
```


Now get all counties, in this instance in the US. Variables: 

* `return_region_type`: [subnational2|subnational1|country]. The type of subregions to be returned.
* `parent_region_code`: any ISO3166 subnational1 or country code, or 'world'. If 'world' then regionType must be 'country'.
* `json_or_csv`: [json|csv]. Suffix to specify result content type.

```{r}
library("httr")
library("dplyr")

ebase <- 'https://ebird.org/ws2.0/'
return_region_type <- 'subnational2'
parent_region_code <- "US"
args <- list('X-eBirdApiToken' = EBIRD_KEY)
json_or_csv <- 'csv'
    
url <- paste0(ebase, 'ref/region/list/', return_region_type, '/', parent_region_code, '.', json_or_csv)

ret <- GET(url, add_headers("X-eBirdApiToken" = EBIRD_KEY)) #, query = args)
ret
```

Transform this return into a tibble:
```{r}
asChar <- readBin(ret$content, "character")
counties <- tbl_df(read.delim(text = asChar, sep=',',
                              stringsAsFactors = FALSE))
counties
```

Get frequencies for one county

```{r}
library("rebird")

county_freqs <- ebirdfreq(loc = 'US-SC-001', loctype='counties', date='2019-02-14',max=10) #TODO what does date mean 

county_freqs
```

Get frequencies for all counties..

```{r}
t0 <- proc.time()
csv_path = './county_results/'
num_counties = 10
total_counties = dim(counties)[1]
for (i in 1:dim(counties)[1]) {
  county_code <- counties[[i,1]]
  result <- ebirdfreq(loc = county_code, loctype='counties')#, date='2019-02-14',max=10)
  write.csv(result, file = paste0(csv_path, county_code, '.csv'))
}
t1 <- proc.time()
total_time <- t1 - t0
print("Time elapsed:")
print(total_time)
```

Remove certain species from consideration by common name:

```{r}
spp_to_remove <- list("Snow Goose", "Ross's Goose")

subset_county_freqs <- subset(county_freqs, comName != spp_to_remove)
subset_county_freqs
```


